Low Complexity Adaptive Sonar Imaging

### 2016-03-02 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2016:03:02	18:04:38	(on. 2.mars)

\newif\ifBuildBibliography\BuildBibliographyfalse  % Whether to include the references.bib file or use inline references.

@@

To build confidence in the LCA method we show that a robust MVDR implementation typically creates weights spanning between the rectangular and Hamming window function. We let LCA select from a set of Kaiser windows with responses in this span, and add some steered variations of each. We limit the steering to roughly half the \minus{}3\,dB width of the window's amplitude response. Using experimental data from the Kongsberg Maritime HISAS1030 sonar we find that LCA and MVDR produce nearly identical images of large scenes, both being superior to DAS. On point targets LCA is able to double the resolution compared to DAS, or provide half that of MVDR. This performance is achieved with a total of 6 windows; the rectangular and Kaiser window with $\beta=5$, in unsteered version, and left and right steered to the steering limit. Slightly smoother images are produced if the window count is increased to 15, but past this we observe minimal difference. Finally we show that LCA works just as well if Kaiser windows are substituted with trigonometric ones.

@@

A much faster and simpler alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. Based on an idea by Vignon~\cite{Vignon2008}, it was first introduced by Synnev\aa{}g \emph{et al}. in clinical medical ultrasound imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar image quality to MVDR in systems with focused transmit beams. LCA applies a set of predefined and static windows, or apodization weights, and selects the one offering the best noise suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a discrete and static window solution space. Alternatively, it may be viewed as a multi-apodization technique. One such method is described by Stankwitz \emph{et al}. in radar imaging~\cite{Stankwitz1995}, where the best out of 2 or 3 windows are selected. However, LCA is different in that it typically selects from a larger pool of windows and allows phase-steered variations of them. This gives LCA an adaptive freedom that lies somewhere in between that of traditional multi-apodization techniques and MVDR. How similarly LCA performs compared to MVDR depends on how well the predefined windows represent the constrained solution space of MVDR.

@@

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/buske3_online.pdf}%
\caption{\emph{Determining LCA window type}: MVDR image with typical frequency responses for windows used in various pixel regions.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, with the pixel groups are indicated with red boxes.}\protect\\\hspace{\textwidth}
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{MVDR window amplitude and phase responses computed from 40x40 pixel groups to provide sufficient statistics for the shadow, highlight and speckle region of the image. The responses are overlayed each other and the amount of overlap is colored using a logarithmic scale. Since each pixel is pre-delayed into focus the unsteered responses all have their center at broadside. The dashed red lines at -13\,dB and -43\,dB marks the peak sidelobe levels of an unsteered rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3\,dB in highlight. The phase varies most in the highlight region where we see the highest contrast.} }\label{mvdr_selected_windows}
\end{figure*}

@@

Unlike the method described by Synnev\aa{}g~\cite{Synnevag2008} we do not let LCA choose from inverted Kaiser windows. These have a mainlobe width narrower than that of the rectangular window, but at the expense of a very poor white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions of them. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of \minus{}13\,dB.

>>>>

\newif\ifBuildBibliography\BuildBibliographytrue  % Whether to include the references.bib file or use inline references.

@@

To build confidence in the LCA method we show that a robust MVDR implementation typically creates weights spanning between the rectangular and Hamming window function. We let LCA select from a set of Kaiser windows with responses in this span, and add some steered variations of each. We limit the steering to roughly half the \minus{}3\,dB width of the window's amplitude response. Using experimental data from the Kongsberg Maritime HISAS1030 sonar we find that LCA and MVDR produce nearly identical images of large scenes, both being superior to DAS. On point targets LCA is able to double the resolution compared to DAS, or provide half that of MVDR. This performance is achieved with a total of 6 windows; the rectangular window and the Kaiser window with $\beta=5$, in an unsteered version, and versions that are left and right steered to the steering limit. Slightly smoother images are produced if the window count is increased to 15, but past this we observe minimal difference. Finally we show that LCA works just as well if Kaiser windows are substituted with trigonometric ones.

@@

A much faster and simpler alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. Based on an idea by Vignon~\cite{Vignon2008}, it was first introduced by Synnev\aa{}g \emph{et al}. in clinical medical ultrasound imaging~\cite{Synnevag2011}, who demonstrated its ability to obtain very similar image quality to MVDR in systems with focused transmit beams. LCA applies a set of predefined and static windows, or apodization weights, and selects the one offering the best noise suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a discrete and static window solution space. Alternatively, it may be viewed as a multi-apodization technique. One such method is described by Stankwitz \emph{et al}. in radar imaging~\cite{Stankwitz1995}, where the best out of 2 or 3 windows are selected. However, LCA is different in that it typically selects from a larger pool of windows and allows phase-steered variations of them. This gives LCA an adaptive freedom that lies somewhere in between that of traditional multi-apodization techniques and MVDR. How similarly LCA performs compared to MVDR depends on how well the predefined windows represent the constrained solution space of MVDR.

@@

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/buske3_online.pdf}%
\caption{\emph{Determining LCA window type}: MVDR image with typical frequency responses for windows used in various pixel regions.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, with the pixel groups are indicated with red boxes.}\protect\\\hspace{\textwidth}
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{MVDR window amplitude and phase responses computed from 40x40 pixel groups for the shadow, highlight and speckle region of the image. The responses are overlayed each other and the amount of overlap is colored using a logarithmic scale. The size of the pixel groups were chosen ad-hoc for the histograms to be near invariant to a shift in position within the same region. Since each pixel is pre-delayed into focus the unsteered responses all have their center at broadside. The dashed red lines at -13\,dB and -43\,dB marks the peak sidelobe levels of an unsteered rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3\,dB in highlight. The phase varies most in the highlight region where we see the highest contrast.} }\label{mvdr_selected_windows}
\end{figure*}

@@

Unlike the method described by Synnev\aa{}g~\cite{Synnevag2011} we do not let LCA choose from inverted Kaiser windows. These have a mainlobe width narrower than that of the rectangular window, but at the expense of a very poor white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions of them. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of \minus{}13\,dB.

### 2016-03-02 LCAforActiveSonarImaging/submission/submit1/answer/answer.tex
la2pdf commit - 2016:03:02	13:56:02	(on. 2.mars)
la2pdf commit - 2016:03:02	16:12:30	(on. 2.mars)
la2pdf commit - 2016:03:02	18:04:38	(on. 2.mars)

\begin{enumerate}
% \emph{General}
\hi{Abstract}
\qi{"the array's spatial covariance matrix" might be a bit shocking for the non-expert Reader $\rightarrow$ The formulation in the Introduction might fit better "the influence of noise ..."}
\ai{This is a good point. We have reformulated the sentence to speak of computing the spatial statistics instead.}
%
\hi{Page 2}
\qi{"6 of which were micro-steered" $\rightarrow$ a short explanation or reference might help to understand what is meant by "micro-steered"}
\ai{Another good point. This wording is now changed and a sentence elaborating on its meaning is added.}
%
\qi{"it was not clear how how many" $\rightarrow$ delete 1 x "how"}
\ai{Thank you. Corrected.}
%
\qi{"with an element beamwidth" $\rightarrow$ what is meant by element beamwidth? Maybe an additional figure could be used to explain this.}
\ai{Good remark. We meant the -3dB opening angle of the elements. We have reworded this the two places it is mentioned.}
%
\hi{Page 3, after (1)}
\qi{"Applying a window that trails off .... Minimum variance distortion-less response (MVDR) beamformer." $\rightarrow$ real and complex Windows? The introduction should be more formal: x ist introduced as delayed data, weights or delays to change, or both is explained later. $\rightarrow$ The difference between noise and sidelobes should be pointed out.}
\ai{}
%
\hi{Page 5, equation (5)}
\qi{The lateral correlation and the reason why equation (5) is a good choice should be better explained.}
\ai{Indeed it should, this paragraph is now rewritten.}
%
\hi{Page 6, last row}
\qi{"they are optimal for any value" $\rightarrow$ optimal in which sense?}
\ai{Thank you. This was mentioned earlier in the same paragraph, just after (8).}
%
\hi{Fig 3}
\qi{why is a 40x40 pixel group a good choice? could the associated broadside direction be made visible in the figure, too?}
\ai{This is an excellent question. This should perhaps be related to the detail level in the image, which in turn depends on the array's imaging performance.}
%
\hi{Page 8}
\qi{reference to Fig.1 $\rightarrow$ could the sequence of figures be changes to have Fig. 1 closer to this paragraph}
\ai{Valid point. In our two column print the figure is on the page before its first reference. }
%
\hi{Page 11}
\qi{where is the synthetic aperture needed/applied in this work, or is it just the name of the array? how does the work on LCA/MVDR Change the Quality of synthetic aperture? What exactly is the sectorscan mode?}
\ai{The reviewer is quite right, it is a system designed for SAS imaging, but we only create image sectors for its data. That is, the images are from single ping, rather than synthesized from several pings. We agree this was worded in an ambiguous way and have now made relevant changes, as well as added a remark of what it meant by sectorscan.}
%
\end{enumerate}

\subsection*{Suggestions for improving the exposition of the processing}

@@

\begin{enumerate}
\item Fig 8 is new. It was added to provide details on how the steering bound $\phi_\mathrm{3dB}$ is affected by the number of elements $M$ and the element spacing relative to the wavelength $\frac{d}{\lambda}$.
\end{enumerate}

@@

The steering bound $\phi_\mathrm{3dB}$ depends on not just $\beta$, but also on the number of elements $M$ and the element spacing relative to the wavelength $\frac{d}{\lambda}$.
\begin{enumerate}
\item We have supplied additional info on how the steering is affected by these parameters in appendix C.
\item Equations (12) and (14) only gave the correct results for our system configuration, and were not very intuitive. Appendix C now replace and extends these equations, and we removed them in hope this will make the article easier to read.
\end{enumerate}

>>>>

\begin{enumerate}
% \emph{General}
\hi{Abstract}
\qi{"the array's spatial covariance matrix" might be a bit shocking for the non-expert Reader $\rightarrow$ The formulation in the Introduction might fit better "the influence of noise ..."}
\ai{This is a good point. We have reformulated the sentence to speak of computing the spatial statistics instead.}
%
\hi{Page 2}
\qi{"6 of which were micro-steered" $\rightarrow$ a short explanation or reference might help to understand what is meant by "micro-steered"}
\ai{Another good point. This wording is now changed and a sentence elaborating on its meaning is added.}
%
\qi{"it was not clear how how many" $\rightarrow$ delete 1 x "how"}
\ai{Thank you. Corrected.}
%
\qi{"with an element beamwidth" $\rightarrow$ what is meant by element beamwidth? Maybe an additional figure could be used to explain this.}
\ai{Good remark. We meant the -3dB opening angle of the elements. We have reworded this the two places it was mentioned.}
%
\hi{Page 3, after (1)}
\qi{"Applying a window that trails off .... Minimum variance distortion-less response (MVDR) beamformer." $\rightarrow$ real and complex Windows? The introduction should be more formal: x ist introduced as delayed data, weights or delays to change, or both is explained later. $\rightarrow$ The difference between noise and sidelobes should be pointed out.}
\ai{Good observations. We realize this was ambiguous and have now rewritten this paragraph in hopes it will be clearerr.}
%
\hi{Page 5, equation (5)}
\qi{The lateral correlation and the reason why equation (5) is a good choice should be better explained.}
\ai{Indeed. We have rewritten the paragraph slightly, but the technique is mentioned mostly for completeness. It wasn't used.}
%
\hi{Page 6, last row}
\qi{"they are optimal for any value" $\rightarrow$ optimal in which sense?}
\ai{Thank you. This was mentioned earlier in the same paragraph, just after (8). Is this insufficient?}
%
\hi{Fig 3}
\qi{why is a 40x40 pixel group a good choice? could the associated broadside direction be made visible in the figure, too?}
\ai{This is an excellent question. This should perhaps be related to the detail level in the image, which in turn depends on the array's imaging performance. We took an ad-hoc approach to this and selected 40x40 pixels to get sufficient statistics for a visually good looking histogram. We have now written this into the caption of Fig. 3.}
%
\hi{Page 8}
\qi{reference to Fig.1 $\rightarrow$ could the sequence of figures be changes to have Fig. 1 closer to this paragraph}
\ai{We agree this would be better. In our two column print the figure is on the page before its first reference. We assume this will be placed properly when processed for publishing.}
%
\hi{Page 11}
\qi{where is the synthetic aperture needed/applied in this work, or is it just the name of the array? how does the work on LCA/MVDR Change the Quality of synthetic aperture? What exactly is the sectorscan mode?}
\ai{The reviewer is quite right, it is a system designed for SAS imaging, but we only create image sectors for its data. That is, the images are from single ping, rather than synthesized from several pings. We agree this was worded in an ambiguous way and have now made relevant changes, as well as added a remark of what it meant by sectorscan.}
%
\end{enumerate}

@@

\begin{enumerate}
\item Fig 3. Caption changed to indicate that the size 40x40 pixels was chosen for sufficient statistics to make the histogram look well. Also added a sentence explaining that the steering is relative to broadside for all pixels, since each of them are pre-delayed into focus.
\item Fig 8 is new. It was added to provide details on how the steering bound $\phi_\mathrm{3dB}$ is affected by the number of elements $M$ and the element spacing relative to the wavelength $\frac{d}{\lambda}$.
\end{enumerate}

@@

\begin{enumerate}
\item The steering bound $\phi_\mathrm{3dB}$ depends on not just $\beta$, but also on the number of elements $M$ and the element spacing relative to the wavelength $\frac{d}{\lambda}$. 
\begin{enumerate}
\item We have supplied additional info on how the steering is affected by these parameters in appendix C.
\item Equations (12) and (14) only gave the correct results for our system configuration, and were not very intuitive. Appendix C now replace and extends these equations, and we removed them in hope this will make the article easier to read.
\end{enumerate}
\item Various spelling flaws attempted corrected.
\item Appendix C added. Contains information of where source code and media files can be located. Before the article goes to publishing we will make sure that this link is permanent.
\end{enumerate}
